\LARGE \bf Towards a Data-driven Approach to Motion Planning

### 2015-02-26 paper2015asml.tex
fixed typos

Recent work has also addressed the task of making motions predictable (similar motions in similar environments and tasks) and/or legible (make it easier for human observers to understand the intent of the robot)~\cite{Beetz:2010}. Legibility makes it possible for human observers to understand clearly what a robot is intending to do, allowing them to modify their actions and motions if necessary. Predictability implies that the robot will always be consistent in its actions, removing the element of surprise for human observers. These concepts have been well-studies recently with the intent of measuring legibility~\cite{Lichtenthaler:2011}, using expressions to improve the readability of robots~\cite{Takayama:2011} and generating anticipation~\cite{Gielniak:2011}. In~\cite{Dragan:2013}, the notion of legibility was incorporated into a constrained trajectory optimization motion planner to generate motions that are more legible to human observers,\hl{ while in}~\cite{mainprice2011planning} \hl{a cost-map was developed in conjunction with sampling based planning to produce trajectories in cluttered ienvironements.}

There has been relatively little examination of how human observers perceive robot arm trajectories in environments with obstacles. There is no data available for how human observers react to such robot motions. It is not clear whether minimum-jerk trajectories (or other cost functions) are the best descriptors of motions in such environments or if there are other features that better explain human-observer preferences in such sitations. Our goal in this work is to collect the data needed to answer the query, ``Which robot trajectories in cluttered environments do human-observers prefer'' A second question that we would like to answer is ``Why are certain robot trajectories preferred by human-observers?'' This is a larger question that we aim to address in future work and instead we focus on, ``Can we predict a human-observer preference for a given trajectory'' The answer to this latter question, we hope, will eventually point us towards trajectories that are better accepted by human observers.

@@

We conducted an online survey\footnote{The online survey was conducted after gaining a waiver from SRI's IRB after a review of our survey procedure. Our survey followed standard guidelines for privacy of respondent information when conducting a survey on Mechanical Turk.} where we asked human observers to rate a variety of trajectories of the PR2 robot. The survey was built on Amazon's Mechanical Turk, which has become a useful tool for large online data gathering and crowd-sourced work. Each respondent in the survey was presented with a set of demographic questions, a video, and asked to rate the robot's motion on the attributes  of elegance, efficency, smoothness and overall impression (a summary of the rating scales used in the main survey question can be seen in Table~\ref{tab:rating_scales}). The ratings were later converted into numerical values on a scale of 1 to 7. Each respondent was expected to rate multiple trajectories but could not rate a trajectory more than once. Each video has four different views of the robot displayed simultaneously. Respondents were asked demographic questions about familiarity with video games, familiarity with robotics, age group and highest education level. The demographic information was not used to filter the responses we collected.

@@

\rot{wrist\_bfs\_dtw} & 
\adjincludegraphics[trim={.1\width} {.0\height} {.1\width} {.0\height}, clip, width=0.4\columnwidth]{\fta{wrist_bfs_dtw}{low}{0}} & 
\adjincludegraphics[trim={.1\width} {.0\height} {.1\width} {.0\height}, clip, width=0.4\columnwidth]{\fta{wrist_bfs_dtw}{high}{0}} \\
\hline
\end{tabular}
\caption{Example trajectories for different values of the most useful features. Trajectories on the left have low feature values while trajectories on the right have high features values for each corresponding feature in that row.}\label{fig:example_features}
\vspace{-0.2in} 
\end{figure}

@@

The second classification framework we use is a random forest ensemble of trees. This involves randomly dividing the data into several bootstrap training samples and building a tree on each bootstrap sample. Within each boostrapped sample, at each split a subset of features is randomly selected from the full set of features, but only one predictor is used at each split. This brings additional randomness within each tree. The class is chosen by majority vote across all trees. For every tree constructed from a bootstrapped training sample there is one Out of Bag (OOB) error which can be thought of as a test error for every tree. It is estimated internally, during the run. On test data, the random forest method returns 83\% accuracy.

>>>>

Recent work has also addressed the task of making motions predictable (similar motions in similar environments and tasks) and/or legible (make it easier for human observers to understand the intent of the robot)~\cite{Beetz:2010}. Legibility makes it possible for human observers to understand clearly what a robot is intending to do, allowing them to modify their actions and motions if necessary. Predictability implies that the robot will always be consistent in its actions, removing the element of surprise for human observers. These concepts have been well-studied recently with the intent of measuring legibility~\cite{Lichtenthaler:2011}, using expressions to improve the readability of robots~\cite{Takayama:2011} and generating anticipation~\cite{Gielniak:2011}. In~\cite{Dragan:2013}, the notion of legibility was incorporated into a constrained trajectory optimization motion planner to generate motions that are more legible to human observers,\hl{ while in}~\cite{mainprice2011planning} \hl{a cost-map was developed in conjunction with sampling based planning to produce trajectories in cluttered ienvironements.}

There has been relatively little examination of how human observers perceive robot arm trajectories in environments with obstacles. There is no data available for how human observers react to such robot motions. It is not clear whether minimum-jerk trajectories (or other cost functions) are the best descriptors of motions in such environments or if there are other features that better explain human-observer preferences in such sitations. Our goal in this work is to collect the data needed to answer the query, ``Which robot trajectories in cluttered environments do human-observers prefer'' A second question that we would like to answer is ``Why are certain robot trajectories preferred by human-observers?'' This is a larger question that we aim to address in future \hl{work. Instead we} focus on answering ``Can we predict a human-observer preference for a given trajectory'' The answer to this latter question, we hope, will eventually point us towards trajectories that are better accepted by human observers.

@@

We conducted an online survey\footnote{The online survey was conducted after gaining a waiver from SRI's IRB after a review of our survey procedure. Our survey followed standard guidelines for privacy of respondent information when conducting a survey on Mechanical Turk.} where we asked human observers to rate a variety of trajectories of the PR2 robot. The survey was built on Amazon's Mechanical Turk, which has become a useful tool for large online data gathering and crowd-sourced work. Each respondent in the survey was presented with a set of demographic questions, a video, and asked to rate the robot's motion on the attributes  of elegance, efficiency, smoothness and overall impression (a summary of the rating scales used in the main survey question can be seen in Table~\ref{tab:rating_scales}). The ratings were later converted into numerical values on a scale of 1 to 7. Each respondent was expected to rate multiple trajectories but could not rate a trajectory more than once. Each video has four different views of the robot displayed simultaneously. Respondents were asked demographic questions about familiarity with video games, familiarity with robotics, age group and highest education level. The demographic information was not used to filter the responses we collected.

@@

\rot{wrist\_bfs\_dtw} & 
\adjincludegraphics[trim={.1\width} {.0\height} {.1\width} {.0\height}, clip, width=0.4\columnwidth]{\fta{wrist_bfs_dtw}{low}{0}} & 
\adjincludegraphics[trim={.1\width} {.0\height} {.1\width} {.0\height}, clip, width=0.4\columnwidth]{\fta{wrist_bfs_dtw}{high}{0}} \\
\hline
\end{tabular}
\caption{Example trajectories for different values of the most useful features. \hl{Trajectories on the left have low-end value while trajectories on the right have high-end value for each corresponding feature in that row.}}\label{fig:example_features}
\vspace{-0.2in} 
\end{figure}

@@

The second classification framework we use is a random forest ensemble of trees. This involves randomly dividing the data into several bootstrap training samples and building a tree on each bootstrap sample. Within each bootstrapped sample, at each split a subset of features is randomly selected from the full set of features, but only one predictor is used at each split. This brings additional randomness within each tree. The class is chosen by majority vote across all trees. For every tree constructed from a bootstrapped training sample there is one Out of Bag (OOB) error which can be thought of as a test error for every tree. It is estimated internally, during the run. On test data, the random forest method returns 83\% accuracy.
